---
title: "analysis"
author: "Jamie Cummins"
date: "13/3/2019"
output: html_document
---

```{r include=FALSE}
knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE, 
                      cache = TRUE,
                      echo = FALSE)

```

```{r}
library(tidyverse)
library(lme4)
library(sjPlot)

demographics_df <- read_csv("../data/processed/demographics.csv")
fort_df         <- read_csv("../data/processed/fort.csv")
```

```{r}
race_comparisons_df <- fort_df %>%
  filter(trialcode == "black" | trialcode == "white") %>%
  mutate(condition = 
           case_when(trialcode == "white" ~ 1,
                     trialcode == "black" ~ 2)) %>%
  dplyr::rename(pleasant_response = correct) %>%
  mutate(condition = as.factor(condition))

valence_comparisons_df <- fort_df %>%
  filter(trialcode == "pleasant" | trialcode == "unpleasant") %>%
  mutate(condition = 
           case_when(trialcode == "pleasant" ~ 1,
                     trialcode == "unpleasant" ~ 2)) %>%
  dplyr::rename(pleasant_response = correct) %>%
  mutate(pleasant_response = ifelse(trialcode == "unpleasant" & 
                                    pleasant_response == 1, 0,
                             ifelse(trialcode == "unplesaant" & 
                                    pleasant_response == 0, 1, 
                                    pleasant_response))) %>%
  mutate(condition = as.factor(condition))

neutral_comparisons_df <- fort_df %>%
  filter(trialcode == "neutral") %>%
  mutate(condition = 
           case_when(stimulusitem1 == "N106.bmp" ~ 1,
                     stimulusitem1 == "N092.bmp" ~ 2,
                     stimulusitem1 == "N101.bmp" ~ 1,
                     stimulusitem1 == "N011.bmp" ~ 2,
                     stimulusitem1 == "N089.bmp" ~ 1,
                     stimulusitem1 == "N020.bmp" ~ 2,
                     stimulusitem1 == "N039.bmp" ~ 1, 
                     stimulusitem1 == "N061.bmp" ~ 2,
                     stimulusitem1 == "N081.bmp" ~ 1,
                     stimulusitem1 == "N102.bmp" ~ 2)) %>%
  dplyr::rename(pleasant_response = correct) %>%
  mutate(condition = as.factor(condition))

gender_comparisons_df <- fort_df %>%
  filter(trialcode == "black" | trialcode == "white") %>%
  mutate(condition = 
           case_when(stimulusitem1 == "white1.png" ~ 1,
                     stimulusitem1 == "white2.png" ~ 1,
                     stimulusitem1 == "black1.png" ~ 1,
                     stimulusitem1 == "black2.png" ~ 1,
                     stimulusitem1 == "white3.png" ~ 2,
                     stimulusitem1 == "white4.png" ~ 2,
                     stimulusitem1 == "black3.png" ~ 2, 
                     stimulusitem1 == "black4.png" ~ 2)) %>%
  dplyr::rename(pleasant_response = correct) %>%
  mutate(condition = as.factor(condition))
```

# M1: Do we see the correct response mappings?

```{r}
m1_fit <- glmer(pleasant_response ~ condition + (1 | subject), 
                data = valence_comparisons_df)
tab_model(m1_fit, show.std = TRUE)
plot_model(m1_fit, type = "pred", terms = "condition")

```

# H1: Are neutral images neutral?

```{r}
h1_fit <- glmer(pleasant_response ~ condition + (1 | subject), 
                data = neutral_comparisons_df)
tab_model(h1_fit, show.std = TRUE)
plot_model(h1_fit, type = "pred", terms = "condition")

```

# H2: Do we see evidence for implicit racial bias?

```{r}
h2_fit <- glmer(pleasant_response ~ condition + (1 | subject), 
                data = race_comparisons_df)
tab_model(h2_fit, show.std = TRUE)
plot_model(h2_fit, type = "pred", terms = "condition")

```

# H3: Do we see evidence for implicit gender bias?

```{r}
h3_fit <- glmer(pleasant_response ~ condition + (1 | subject), 
                data = gender_comparisons_df)
tab_model(h3_fit, show.std = TRUE)
plot_model(h3_fit, type = "pred", terms = "condition")

```

# Increase strictness

So no real evidence for any effect. What if we exclude participants who seemed to respond very consistently with either the z or m key?

## Cleaning

```{r}
stricter_subjects_df <- neutral_comparisons_df %>%
  dplyr::count(subject, pleasant_response) %>%
  filter(55 > n, n > 20)
```

```{r}
race_comparisons_stricter_df <- race_comparisons_df %>%
  semi_join(stricter_subjects_df)

valence_comparisons_stricter_df <- valence_comparisons_df %>%
  semi_join(stricter_subjects_df)

neutral_comparisons_stricter_df <- neutral_comparisons_df %>%
  semi_join(stricter_subjects_df)

gender_comparisons_stricter_df <- gender_comparisons_df %>%
  semi_join(stricter_subjects_df)
```

## M1: Do we see the correct response mappings?

```{r}
m1_strict_fit <- glmer(pleasant_response ~ condition + (1 | subject), 
                data = valence_comparisons_stricter_df)
tab_model(m1_strict_fit, show.std = TRUE)
plot_model(m1_strict_fit, type = "pred", terms = "condition")

```

## H1: Are neutral images neutral?

```{r}
h1_strict_fit <- glmer(pleasant_response ~ condition + (1 | subject), 
                data = neutral_comparisons_stricter_df)
tab_model(h1_strict_fit, show.std = TRUE)
plot_model(h1_strict_fit, type = "pred", terms = "condition")

```

## H2: Do we see evidence for implicit racial bias?

```{r}
h2_strict_fit <- glmer(pleasant_response ~ condition + (1 | subject), 
                data = race_comparisons_stricter_df)
tab_model(h2_strict_fit, show.std = TRUE)
plot_model(h2_strict_fit, type = "pred", terms = "condition")

```

## H3: Do we see evidence for implicit gender bias?

```{r}
h3_strict_fit <- glmer(pleasant_response ~ condition + (1 | subject), 
                data = gender_comparisons_stricter_df)
tab_model(h3_strict_fit, show.std = TRUE)
plot_model(h3_strict_fit, type = "pred", terms = "condition")

```







